Practical Open-Loop Optimistic Planning

### 2019-08-30 paper/main.tex
Fix typo in image name
Updates from Overleaf

\begin{figure}[htp]
\centering
%\begin{minipage}{\textwidth}
%      \includegraphics[width=\textwidth]{img/hw_return_svg-tex}
%      \label{sub:highway}
%      \includegraphics[width=0.5\textwidth]{img/gw_return_svg-tex}
%      \label{sub:gridworld}
%      \includegraphics[width=0.5\textwidth]{img/gw_stoch_return_svg-tex}
%      \label{sub:gridworld_stoch}

\subfloat{
	\includegraphics[width=0.33\textwidth]{img/hw_return_svg-tex}
	\label{sub:highway}
}
\subfloat{
	\includegraphics[width=0.33\textwidth]{img/gw_return_svg-tex}
	\label{sub:gridworld}
}
\subfloat{
	\includegraphics[width=0.33\textwidth]{img/gw_stoch_return_svf-tex}
	\label{sub:gridworld_stoch}
}
    \caption{Numerical experiments: for each environment-agent configuration, we compute the average return over 100 runs –- along with its 95\% confidence interval –- with respect to the available budget $n$.}
    \label{fig:experiments}
%\end{minipage}
\end{figure}

\begin{figure}[pht]
	\centering

	\includegraphics[width=0.43\textwidth]{img/tree-ODP_svg-tex} \includegraphics[width=0.43\textwidth]{img/tree-OLOP_svg-tex}
	\includegraphics[width=0.43\textwidth]{img/tree-KL-OLOP_svg-tex}

>>>>

\begin{figure}[pth]
\centering
\subfloat{
	\includegraphics[width=\textwidth]{img/hw_return_svg-tex}
	\label{sub:highway}
}
\newline
\subfloat{
	\includegraphics[width=0.49\textwidth]{img/gw_return_svg-tex}
	\label{sub:gridworld}
}
\subfloat{
	\includegraphics[width=0.49\textwidth]{img/gw_stoch_return_svg-tex}
	\label{sub:gridworld_stoch}
}
    \caption{Numerical experiments: for each environment-agent configuration, we compute the average return over 100 runs –- along with its 95\% confidence interval –- with respect to the available budget $n$.}
    \label{fig:experiments}
%\end{minipage}
\end{figure}

\begin{figure}[pth]
	\centering

	\includegraphics[width=0.64\textwidth]{img/tree-ODP_svg-tex} \includegraphics[width=0.64\textwidth]{img/tree-OLOP_svg-tex}
	\includegraphics[width=0.64\textwidth]{img/tree-KL-OLOP_svg-tex}

### 2019-08-30 paper/poster/poster.tex
Updates from Overleaf

\documentclass[paperwidth=36in, paperheight=48in,portrait,fontscale=0.35, margin=2cm]{baposter}

@@

%\background{ % Set the background to an image (background.pdf)
%\begin{tikzpicture}[remember picture,overlay]
%\draw (current page.north west)+(-2em,2em) node[anchor=north west]
%{\includegraphics[height=1.1\textheight]{background.png}};
%\end{tikzpicture}
%}
\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
boxColorOne=boxcolor, % Background color for the content in the content boxes
headershape=roundedright, % Specify the rounded corner in the content box headers
%headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
headerfont=\Large\bf\textsc, %Sans Serif
textborder=rectangle,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain,
textfont={\setlength{\parindent}{0.0em}\sffamily},
headerheight={0.05\textheight},
eyecatcher=true
%columns=5
}
%
%----------------------------------------------------------------------------------------
%	Title and authors
%----------------------------------------------------------------------------------------
%
{
\includegraphics[width=14em]{./img/renault_group}
}
{
Practical Open-Loop Optimistic Planning
}
{
Edouard Leurent, Odalric-Ambrym Maillard
\vspace{-3\baselineskip}
}
{
\includegraphics[width=14em]{./img/inria_sc}
}

@@

We consider the optimal control of an MDP $\cM = (\cS, cA, R, T, \gamma)$ with bounded rewards $R$
\begin{itemize}[nolistsep]
    \item[\incarrow] $R$ and $T$ are \hlr{unknown}
    \item[\incarrow] Access to a \hlb{generative model} $s' \sim \probability{s'|s,a}$ and $r\sim\probability{r|s, a}$
    \item[\incarrow] \hlr{Fixed-budget} setting: the generative model is \hlr{costly}, can only be queried $n$ times
\end{itemize}
}

@@

\begin{center}
    \hlb{Optimism in the Face of Uncertainty}\\
    \incarrow~ in \hlr{observed} and \hlr{future} rewards

\end{center}
%Split the budget $n$ into $M$ sequences of length $L$.
%Let $M$ be the largest integer such that $M \log M/(2 \log 1/\gamma) \leq n$\;
%Let $L = \log M / (2 \log 1/\gamma)$\;

\includesvg[width=\textwidth]{img/olop-explain.svg}
\includesvg[width=\textwidth]{img/olop-explain-2.svg}

@@

\includesvg[width=\textwidth]{img/olop-explain-3.svg}

@@

\begin{minipage}[]{0.59\textwidth}
 We summon the upper-confidence bound from \texttt{kl-UCB} [\cite{Cappe2013}]:
    \begin{equation*}
        U^{\mu}_a(m) \eqdef \max \left\{q\in I: T_a(m) d(\hat{\mu}_a(m), q) \leq f(m) \right\}
    \end{equation*}

@@

%
%%----------------------------------------------------------------------------------------
%% Experiments
%%----------------------------------------------------------------------------------------
%
\headerbox{Experiments}{name=experiments,span=2,column=1,below=time, above=bottom}{

\textbf{Expanded trees} for a budget $n=10^3$

    \includesvg[width=0.33\textwidth]{../img/tree-ODP}    \includesvg[width=0.33\textwidth]{../img/tree-OLOP}
    \includesvg[width=0.33\textwidth]{../img/tree-KL-OLOP}

\textbf{Average return} over 100 runs –- along with its 95\% confidence interval –- with respect to the available budget $n$

     \includesvg[width=0.33\textwidth]{../img/hw_return}
     \includesvg[width=0.33\textwidth]{../img/gw_return}
     \includesvg[width=0.33\textwidth]{../img/gw_stoch_return}
}

>>>>

\documentclass[a0paper,portrait,fontscale=0.35, margin=2cm]{baposter}

@@

%\background{ % Set the background to an image (background.pdf)
%\begin{tikzpicture}[remember picture,overlay]
%\draw (current page.north west)+(-2em,2em) node[anchor=north west]
%{\includegraphics[height=1.1\textheight]{background.png}};
%\end{tikzpicture}
%}
\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
boxColorOne=boxcolor, % Background color for the content in the content boxes
headershape=roundedright, % Specify the rounded corner in the content box headers
%headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
headerfont=\Large\bf\textsc, %Sans Serif
textborder=rectangle,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain,
textfont={\setlength{\parindent}{0.0em}\sffamily},
headerheight={0.05\textheight},
eyecatcher=true
%columns=5
}
%
%----------------------------------------------------------------------------------------
%	Title and authors
%----------------------------------------------------------------------------------------
%
{
\includegraphics[width=14em]{./img/renault_group}
}
{
Practical Open-Loop Optimistic Planning
}
{
Edouard Leurent, Odalric-Ambrym Maillard
\vspace{-4\baselineskip}
}
{
\includegraphics[width=14em]{./img/inria_sc}
}

@@

We consider the optimal control of an MDP $\cM = (\cS, A, R, T, \gamma)$ with bounded rewards $R\in[0,1]$
\begin{itemize}[nolistsep]
    \item[\incarrow] $R$ and $T$ are \hlr{unknown}
    \item[\incarrow] Access to a \hlb{generative model} $s' \sim \probability{s'|s,a}$ and $r\sim\probability{r|s, a}$
    \item[\incarrow] \hlr{Fixed-budget} setting: the generative model is \hlr{costly}, can only be queried $n$ times
\end{itemize}
}

@@

%Split the budget $n$ into $M$ sequences of length $L$.
%Let $M$ be the largest integer such that $M \log M/(2 \log 1/\gamma) \leq n$\;
%Let $L = \log M / (2 \log 1/\gamma)$\;
\begin{enumerate}
    \item Sample $M$ sequences of actions of fixed length $L$
    \begin{center}
\includesvg[width=0.8\textwidth]{img/olop-explain.svg}
\end{center}
    \item Use the \hlb{return structure} to \hlb{generalise} to unseen sequences
    \begin{center}
\includesvg[width=0.8\textwidth]{img/olop-explain-2.svg}
\end{center}
\item Be \hlb{Optimistic in the Face of Uncertainty}\\
    \incarrow~ in \hlr{observed} and \hlr{future} rewards
\end{enumerate}

@@

\begin{center}
\includesvg[width=0.8\textwidth]{img/olop-explain-3.svg}    
\end{center}

@@

\begin{minipage}[]{0.59\textwidth}
 We summon the upper-confidence bound from \texttt{kl-UCB} [\cite{Cappe2013}]:
    \begin{equation*}
        U^{\mu}_a(m) \eqdef \max \left\{q\in I: d(\hat{\mu}_a(m), q) \leq \frac{f(m)}{T_a(m)} \right\}
    \end{equation*}

@@

%
%%----------------------------------------------------------------------------------------
%% Experiments
%%----------------------------------------------------------------------------------------
%
\headerbox{Experiments}{name=experiments,span=2,column=1,below=time, above=bottom}{ 
     \includesvg[width=0.33\textwidth]{../img/hw_return}
     \includesvg[width=0.33\textwidth]{../img/gw_return}
     \includesvg[width=0.33\textwidth]{../img/gw_stoch_return}
     \begin{center}
         \textbf{Average return} over 100 runs –- along with its 95\% confidence interval –- with respect to the available budget $n$
     \end{center}

    \includesvg[width=0.33\textwidth]{../img/tree-ODP}    \includesvg[width=0.33\textwidth]{../img/tree-OLOP}
    \includesvg[width=0.33\textwidth]{../img/tree-KL-OLOP}
    \begin{center}
        \textbf{Expanded trees} for a budget $n=10^3$
    \end{center}
}
